### 2011-12-04 plos_template.tex
finished survey-results

67.7 \% of all participants would share their data with their DTC-company without any constraints, 25.8 \% would do so, if the company does not share the data with third parties. 6.6 \% of the participants would not share their data. There is no significant difference between sharing-habits between both chromosomal sexes (Somers-d). Those who are a customer of a DTC company or are planing to become one in the future are more likely to share their results, compared to those who don't plan to get themselves genotyped (Somers-d). 
\subsection*{Subsection 2}

>>>>

67.7 \% of all participants would share their data with their DTC-company without any constraints, 25.8 \% would do so, if the company does not share the data with third parties. 6.6 \% of the participants would not share their data. There is no significant difference between sharing-habits between both chromosomal sexes (Somers-d). Those who are a customer of a DTC company or are planing to become one in the future are more likely to share their results, compared to those who don't plan to get themselves genotyped (Somers-d).

There are significant differences between those people who are already genotyped and those who don't plan to get genotyped: (All those numbers are tukey-hsd test). The first group is more likely to agree to share their information because they want to help scientists (mean difference = 0.465, SE = 0.128, p = 0.001), because they think of personal benefits (mean difference = 0.448, SE = 0.183, p = 0.04) and because they are curious (mean difference = 1.159, SE = 0.193, p < 0.001).

On the other hand those hand those people who are not planning to get genotyped are more likely to not share their data, because they agree to fear discrimination (mean difference = 1.060, SE = 0.195, p < 0.001), because they agree that they feel it is a breach of their privacy (mean difference = 0.821, SE = 0.225, p = 0.001), because agree that they fear negative consequences for their family (mean difference = 0.733, SE = 0.21, p = 0.002) or because they agree that they fear personalized advertising (mean difference = 0.848, SE = 0.208, p < 0.001).

Similarly those people who would share data with their DTC provider are more likely to agree on sharing the data, because they want to help scientists (mean difference = 1.57, SE = 0.199, p < 0.001), because they think of personal benefits (mean difference = 0.951, SE = 0.308, p = 0.006), and because they are curious (mean difference = 1.99, SE = 0.321, p < 0.001).

Those participants who are not planning to get genotyped are more likely to agree to not share their data, because they fear discrimination (mean difference = 1.52, SE = 0.322, p < 0.001), because they feel it is a breach of their privacy (mean difference = 1.871, SE = 0.324, p < 0.001), because they fear consequences for their family (mean difference = 1.146, SE = 0.32, p = 0.001) and because they fear personalized advertising (mean difference =  1.112, SE = 0.357, p = 0.006). 
\subsection*{Subsection 2}
